\documentclass[a4paper,12pt,final,sans]{memoir}

%------------------------------------------------------
%	Pre-amble
%------------------------------------------------------

\usepackage[utf8]{inputenc}
\usepackage{flowfram}
\usepackage[pdftex]{graphicx} 
\usepackage{url} % Allows hyperlinks in docuemnt
\usepackage{paralist}
\usepackage{longtable} % Allows tables to flow over pages
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{ocg-p}

% Page Boarder Settings
\usepackage[top=1cm,left=1cm,right=1cm,bottom=1cm]{geometry}
	\textheight=700px
	
% Page Style
\pagestyle{empty} % Disables page numbers
\frenchspacing % Reduces line space
\tightlists % Reduces spacing in itemize
\renewcommand{\familydefault}{bch} % Font changes
\setlength{\parindent}{0pt} % Disable paragraph indent

% Font
\usepackage[T1]{fontenc}
\usepackage[scaled=.97]{helvet}
\usepackage[lining,scaled=.95]{ebgaramond}

\fontencoding{T1}
\fontseries{c}
\fontshape{n}
\fontfamily{helveticaneue}\selectfont

\fontsize{12}{14}
\selectfont

\renewcommand*\oldstylenums[1]{}

% Define Text Colours
\definecolor{head}{RGB}{49,49,49}
\definecolor{subhead}{RGB}{51,51,51}
\definecolor{module}{RGB}{53,53,53}
\definecolor{body}{RGB}{55,55,55}
\newcommand{\gray}{\rowcolor[gray]{.90}} % Custom highlighting for the work experience and education sections

\makeatletter
\newcommand{\globalcolor}[1]{%
  \color{#1}\global\let\default@color\current@color
}
\makeatother

\AtBeginDocument{\globalcolor{body}}

% Define Background Colour
\definecolor{background}{RGB}{251,251,251}

\begin{ocg}[printocg=never]{Background}{1}{1}
 \pagecolor{background}
\end{ocg}

%PDF MetaData
\pdfinfo{
   /Author   (Nicholas Patten)
   /Title    (N Patten CV)
   /Keywords (LaTeX; 07790200756; nicholaspatten92@gmail.com)
}

%------------------------------------------------------
%	Title Settings
%------------------------------------------------------

\title{\vspace{-2.5cm} \textbf{\textsf{\color{head} Nicholas Patten}}\\}
\date{\vspace{-7.0em}}
\posttitle{\endgroup \vspace{-1em}

\begin{center}
Flat 4, 18 Blackall Road, Exeter, Devon, United Kingdom, \textsc{EX4 4HE}\\ 
\textsc{07790200756}, nicholaspatten92@gmail.com\\
\end{center}}

%------------------------------------------------------
%	Start of document
%------------------------------------------------------

\begin{document} 
\maketitle %Full Name, Address, Mobile Number, Email
\thispagestyle{empty} % Stops make tile, re-enabling page numbers

\vspace{2mm}
%------------------------------------------------------
%	Profile
%------------------------------------------------------
\textbf{\textsf{\color{head} \large{Profile} }} \\[0.3em]
Dev-Ops engineer with over two years of experience in the software industry. Capable of working as part of a team, or independently to fulfill the role. Willing to learn from, and teach others in order to improve delivery of the product. \\

%------------------------------------------------------
%	Techical, computing and additional skills
%------------------------------------------------------

\vskip-2mm

\textbf{\textsf{\color{head} \large{Experience} }}\\[-1.5em]

\begin{itemize}[-]
	\item	{\textbf{\color{module} Languages:} \\[-0.2em]
	Groovy (Gradle \& Jenkins DSL), Java, Javascript, Bash, \textsc{C} }
	 
	\item	{\textbf{\color{module} Frameworks:} \\[-0.2em]
	Grails, Ruby on Rails, Spring}
	
	\item	{\textbf{\color{module} Database \& Database Related:} \\[-0.2em]
	Oracle, \textsc{SQL}, Hibernate, JPA, Data-Modeling}
	
	\item	{\textbf{\color{module} Build Automation \& Continuous Integration:} \\[-0.2em]
	Maven, Gradle, Jenkins, Artifactory}
	
	\item	{\textbf{\color{module} Development \& Testing Tools:} \\[-0.2em]
	JUnit, Powermockito, archaius, Tomcat}
	
	\item	{\textbf{\color{module} IDE's \& Text Editors:} \\[-0.2em]
	Eclipse/\textsc{STS}, NetBeans, Atom, Kate, \textsc{Vim}}
	
	\item	{\textbf{\color{module} Version Control:} \\[-0.2em]
	Git, Mercurial}
	
	\item	{\textbf{\color{module} Markup, Stylesheet and Template Engines:} \\[-0.2em]
	\textsc{XHTML}, \textsc{JSON}, \textsc{CSS}, \textsc{XML}, Freemarker, {\textsc{LaTeX}}}
	
	\item	{\textbf{\color{module} \textsc{OS}:} \\[-0.2em]
	Windows, Mac OSX, Various Linux distributions e.g. Debian, CentOS/Redhat, CoreOs}
\end{itemize}

\vskip1mm

%------------------------------------------------------
%	Employment
%------------------------------------------------------
\textbf{\textsf{\color{head} \large{Employment}}} \\[-0.8em]

\textbf{\textsf{\color{head} Present}} \\[-1.5em]

\iffalse
\begin{longtable}{r p{18cm}}
& \textbf{\textsf{\color{module} \textsc{CMS} Release Manager,}} 
\textsf{\color{head} Mirada, Exeter} |
\textsc{\color{module} \small 2014 - Present} \\[0.5em]

& Responsible for the managerial and development aspects of providing releases of the company's CMS product to various environments to support business continuity.  \\[0.4em]
    
& The management side of this role involves communicating with other teams to ensure that their schedules are on time for the next release and working to resolve any blockers that they may encounter. This requires me to spend a lot of time with staff, working through their build issues, scheduling problems and discussing best implementation methods for designing their service changes.  \\[0.4em]
    
& Very hands on with development, focusing on designing and implementing build processes. This is often programmatically declared using languages such as groovy and bash, which are normally accompanied by Jenkins' jobs. Maintenance and improvement of these processes and scripts are core to the continuous delivery of the product. Often in technical meetings, with various levels of management, around how best to improve our processes and the benefits of the proposed solutions.  \\[0.4em]

& Operational tasks are occasionally required as issues arise in deployment environments, which need to be taken care of before the install process can continue. Acquired good experience with command line and managing Linux based services such as solr, rabbitmq, oracle database, sshd and more. Currently involved in a project, migrating a bricks and mortar system to a cloud-based container system.
	\\[-1.4em]
\end{longtable}
\fi

\begin{longtable}{r p{16cm}}
2014 - 17 & \textbf{\textsf{\color{head} \textsc{CMS} Release Manager, Mirada Exeter}}\\[0.3em]
& Responsible for the managerial and development aspects of providing releases of the company's CMS product to various environments to support business continuity.  \\[0.4em]
    
& The management side of this role involves communicating with other teams to ensure that their schedules are on time for the next release and working to resolve any blockers that they may encounter. This requires me to spend a lot of time with staff, working through their build issues, scheduling problems and discussing best implementation methods for designing their service changes.  \\[0.4em]
    
& Very hands on with development, focusing on designing and implementing build processes. This is often programmatically declared using languages such as groovy and bash, which are normally accompanied by Jenkins' jobs. Maintenance and improvement of these processes and scripts are core to the continuous delivery of the product. Often in technical meetings, with various levels of management, around how best to improve our processes and the benefits of the proposed solutions.  \\[0.4em]

& Operational tasks are occasionally required as issues arise in deployment environments, which need to be taken care of before the install process can continue. Acquired good experience with command line and managing Linux based services such as solr, rabbitmq, oracle database, sshd and more. Currently involved in a project, migrating a bricks and mortar system to a cloud-based container system.
	\\[-1.4em]
	
\end{longtable}

\newpage
\textbf{\textsf{\color{head} Past}} \\[-1.5em]
\begin{longtable}{r p{16cm}}
2013 - 13 & \textbf{\textsf{\color{head} National Museum, Cardiff}}\\[0.3em]
	 & 
	 Short period of work experience, assisting a senior network supervisor. Various skills gained, including managing network cables, cabinets and HP server blades. \\[0.5em]

2011 - 11 & \textbf{\textsf{\color{head} Oxfam, Cardiff}}\\[0.3em]
	 & Charity work as a shop floor assistant and stock organiser. Gained team working skills and customer service experience. \\[0.5em]

2008 - 08 & \textbf{\textsf{\color{head} Maplin’s Electronics, Cardiff}}\\[0.3em]
	 & Work experience as a shop floor assistant. Gained high-quality team working and customer service skills.\\
\end{longtable}

%------------------------------------------------------
%	Education
%------------------------------------------------------
\vspace{-0.5mm}

\textbf{\textsf{\color{head} \large{Education} }}\\[-1.5em]
\begin{longtable}{r p{16cm}}
2011 - 14 & \textbf{\textsf{\color{head} Aberystwyth University;}} Computer Science BSc Hons:\\[0.3em]
		& \textbf{\color{subhead} Major Project;} Ms. Pac-Man Artificial Intelligence Software Controller:\\
		& Researched and developed an autonomous software controller for the video game, Ms Pac-Man game \\[0.2em]

		& \textbf{\color{subhead} Modules:}\\ \defaultlists
		& \textsc{C++}, C And Java Programming Paradigms
		{}\\

		& C And Unix Programming
		{}\\

		& Concepts in Programming
		{}\\

		& Agile Methodologies
		{}\\

		& Software Development Life-cycle
		{}\\

		& Developing Internet Based Applications
		{}\\

		& Modelling Persistent Data
		{}\\

		& Computing Mathematics
		{}\\[0.5em]

2009 - 10 & \textbf{\textsf{\color{head} St David's Catholic College;}} GCE A Level:\\[0.3em]
		& Computing, Film Studies, Welsh Baccalaureate\\[0.5em]

2004 - 09 & \textbf{\textsf{\color{head} St Teilo's CIW High School;}} \textsc{GCSEs:}\\[0.3em]
	 & Nine \textsc{GCSE's}, including: \textsc{IT} (A), \textsc{DT}: Systems and Control (B), English Lang \& Lit (C), Maths (C), Science (C)
\end{longtable}

\vspace{1mm}
%------------------------------------------------------
%	Interests
%------------------------------------------------------
\textbf{\textsf{\color{head} \large{Interests} }} \\[-0.7em]

Fascinated by ever moving technology, always researching embracing the next big thing. Avid video game enthusiast, across multiple platforms. Very sociable and approachable, always up for a company outing and getting to know other members of staff. \\[-0.5em]

%------------------------------------------------------
%	References
%------------------------------------------------------

\textbf{\textsf{\color{head} \large{Referees} }}\\[-0.9em]

References available on request

%\textsc{Richard Jenson, Researcher/ Lecturer at Aberystwyth University, \\
%Department of Computer Science, Aberystwyth University, \\
%Aberystwyth,
%Ceredigion, \textsc{SY23 3DB},
%Wales, \textsc{UK},\\
%\textsc{+44 (0)1970 628510}; rkj@aber.ac.uk\\[-0.7em]

%Jace Tyler, Senior Network Supervisor at the National Museum of Wales,\\
%67 Maes Y Coed Rd, Heath, Cardiff, \textsc{CF4 4HD}, Wales, \textsc{UK},\\
%\textsc{+44 790786352}; jace.tyler@museumwales.ac.uk\\}
\end{document}
